Stable individual differences in strategies within, but not between, visual search tasks

### 2019-10-25 Manuscript/manuscript.tex
fixed a citation (I think)

Previous research has investigated the relationship between these behaviours \textcolor{blue}{and} psychometrics, but to date, these differences have not shown strong correlations with other attributes. \cite{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty. Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}. \textcolor{blue}{However, there is evidence of a link between Attention Deficit/Hyperactivity Disorder and various search behaviours \cite{vandendriessche2019}. Furthermore, the degree to which children exhibit organised scanpaths appears to develop in tandem with executive function \cite{woods2013}.}

>>>>

Previous research has investigated the relationship between these behaviours \textcolor{blue}{and} psychometrics, but to date, these differences have not shown strong correlations with other attributes. Irons and Leber \citeyear{irons-leber2016,irons-leber2018} found no evidence of a correlation between the proportion of optimal choices made by observers in the ACVS paradigm and measures of visual working memory; trait impulsivity; novelty seeking; need for cognition; and intolerance of uncertainty. Similarly, the differences in foraging behaviour are not accounted for by working memory or inhibitory control \cite{johannesson2017}. \textcolor{blue}{However, there is evidence of a link between Attention Deficit/Hyperactivity Disorder and various search behaviours \cite{vandendriessche2019}. Furthermore, the degree to which children exhibit organised scanpaths appears to develop in tandem with executive function \cite{woods2013}.}
